SST_patterns

### 2019-10-08 SST_patterns.Rmd
Plotting Bits

Plot showing upwelling at the different sites for each of the different distances

scatter_func <- function(df){
  CMC_filtered <- df %>%
filter(year(date_start) %in% seq(2010, 2016, 1))
}

CMC_filtered <- scatter_func(df = CMC_upwell_base)
OISST_filtered <- scatter_func(df = OISST_upwell_base)
SACTN_filtered <- scatter_func(df = SACTN_upwell_base)

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(CMC_plot <- plot_scat_func(df = CMC_filtered))
(OISST_plot <- plot_scat_func(df = OISST_filtered))

plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(aes(colour = intensity_cumulative)) + 
  scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  xlab("Date") + ylab("Event duration [days]") 
}

(CMC_plot <- plot_loli_func(df = CMC_filtered))
(OISST_plot <- plot_loli_func(df = OISST_filtered))

@@

>>>>

Plot showing upwelling at the different sites for each of the different distances. Scatter plot

```{r}
library(ggpubr)
year_func <- function(df){
  Filtered <- df %>%
filter(year(date_start) %in% seq(2010, 2016, 1)) 
}

CMC_filtered <- year_func(df = CMC_upwell_base)
OISST_filtered <- year_func(df = OISST_upwell_base)
SACTN_filtered <- year_func(df = SACTN_upwell_base)

CMC_SEAPOINT <- CMC_filtered %>% 
  filter(site == "Sea Point")
CMC_SB <- CMC_filtered %>% 
  filter(site == "Saldanha Bay")
CMC_PN <- CMC_filtered %>% 
  filter(site == "Port Nolloth")
CMC_LB <- CMC_filtered %>% 
  filter(site == "Lamberts Bay")

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(CMC_SP_plot <- plot_scat_func(df = CMC_SEAPOINT))
(CMC_SB_plot <- plot_scat_func(df = CMC_SB))
(CMC_PN_plot <- plot_scat_func(df = CMC_PN))
(CMC_LB_plot <- plot_scat_func(df = CMC_LB))

combined_CMC <- ggarrange(CMC_SP_plot, CMC_SB_plot, CMC_PN_plot,CMC_LB_plot)
###################
## OISST
OISST_SEAPOINT <- OISST_filtered %>% 
  filter(site == "Sea Point")
OISST_SB <- OISST_filtered %>% 
  filter(site == "Saldanha Bay")
OISST_PN <- OISST_filtered %>% 
  filter(site == "Port Nolloth")
OISST_LB <- OISST_filtered %>% 
  filter(site == "Lamberts Bay")

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(OISST_SP_plot <- plot_scat_func(df = OISST_SEAPOINT))
(OISST_SB_plot <- plot_scat_func(df = OISST_SB))
(OISST_PN_plot <- plot_scat_func(df = OISST_PN))
(OISST_LB_plot <- plot_scat_func(df = OISST_LB))
combined_OISST <- ggarrange(OISST_SP_plot, OISST_SB_plot, OISST_PN_plot,OISST_LB_plot)

############## 
# SACTN

@@

# Lolli plot

```{r}
plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(aes(colour = intensity_cumulative)) + 
  scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  xlab("Date") + ylab("Event duration [days]") 
}

(OISST_SP_pl <- plot_loli_func(df = OISST_SEAPOINT))
(OISST_SB_pl <- plot_loli_func(df = OISST_SB))
(OISST_PN_pl <- plot_loli_func(df = OISST_PN))
(OISST_LB_pl <- plot_loli_func(df = OISST_LB))
combined_OISST_pl <- ggarrange(OISST_SP_pl, OISST_SB_pl, OISST_PN_pl,OISST_LB_pl)

#######
# CMC

(CMC_SP_pl <- plot_loli_func(df = CMC_SEAPOINT))
(CMC_SB_pl <- plot_loli_func(df = CMC_SB))
(CMC_PN_pl <- plot_loli_func(df = CMC_PN))
(CMC_LB_pl <- plot_loli_func(df = CMC_LB))
combined_CMC_pl <- ggarrange(CMC_SP_pl, CMC_SB_pl, CMC_PN_pl,CMC_LB_pl)
